Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
Corrected proofs

\begin{lemma}\label{lemma:l2}
Let $p$ and $q$ be arbitrary distributions over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Consider a dataset $D$ of $N$ i.i.d. samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
\begin{equation}\label{eq:lemma2-1}
\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
\end{equation}
\begin{equation}\label{eq:lemma2-2}
\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{equation}
\end{lemma}
\begin{proof}
From Hoeffding's inequality we have:
\begin{align*}
P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2\exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
\end{align*}
which implies that, for any $\delta>0$, with probability at least $1-\delta$:
\begin{align*}
\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
Under independence assumptions, the expected TD error can be re-written as:
\begin{align*}
\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{\wt B_{\bm{w}}}_{\nu}^2,
\end{align*}
where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Thus:
\begin{align}\label{eq:hoeff}
\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align}
From the change of measure inequality \cite{seldin2012pac}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
\begin{align*}
\log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \geq \mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p).
\end{align*}
Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2}$, we obtain:
\begin{align*}
\mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p) \leq \log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \leq 4\frac{R_{max}^2 \lambda^{-1}N}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since the right-hand side of \eqref{eq:hoeff} does not depend on $\bm{w}$. Finally, we can explicitly write:
\begin{align*}
\mathbb{E}_q\left[ \abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
\end{align*}
from which the lemma follows straightforwardly.
\end{proof}

@@

\begin{lemma}\label{lemma:general-bound}
Let $p$ be a prior distribution over the parameter space $\mathcal{W}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Assume $\wh{\xi}$ is the minimizer of $ELBO(\xi) = \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p)$ for a dataset $D$ of $N$ samples. Define $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
\end{lemma}
\begin{proof}
Let us use Lemma \ref{lemma:l2} for the specific choice $q=q_{\wh{\xi}}$. From Eq. \eqref{eq:lemma2-1}, we have:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since $v(\bm{w}) > 0$, while the equality holds from the definition of $\wh{\xi}$. We can now use Eq. \eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right]$, thus obtaining:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
This concludes the proof.
\end{proof}

@@

\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator. Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$. Consider the Gaussian version of Algorithm~\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.~\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d. samples distributed according to $\tau$ and $\nu$. Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
\begin{equation}
\resizebox{0.93\textwidth}{!}{$
\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
\end{equation}
\end{restatable}
\begin{proof}
Using Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}},\wh{\bm{\Sigma}})$, we have:
\begin{align}\label{eq:thg-4}
\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align}
where the second inequality is due to the fact that, since Lemma \ref{lemma:general-bound} contains an infimum over the variational parameters, we can upper bound its right-hand side by choosing any specific $\bm{\xi}$ from $\Xi$. Here, we choose $\bm{\mu} = \bm{w}^*$ and $\bm{\Sigma} = c\bm{I}$, for some positive constant $c>0$. Let us now bound these terms separately.

@@

\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^2 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.

@@

Fix a target task $\tau$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator. Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\abs{\bm{w}}\leq w_{max}$ and uniformly bounded features $\abs{\bm{\phi}(s,a)}\leq \phi_{\max}$. Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior. Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq. \eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d. samples distributed according to $\tau$ and $\nu$. Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:

@@

\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  2\lambda\softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace}{N} + \frac{c_3}{N^2}\right)$},

@@

where $\softmin_i x \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$.

@@

where the inequality holds since the first term is negative. For the second one:

@@

KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \softmin_j\left\lbrace\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right\rbrace.

>>>>

\begin{lemma}\label{lemma:l2}
Let $p$ and $q$ be arbitrary distributions over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Consider a dataset $D$ of $N$ i.i.d. samples where state-action couples are distributed according to $\nu$ and define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\lambda > 0$ and $\delta > 0$, with probability at least $1-\delta$, the following two inequalities hold simultaneously:
\begin{equation}\label{eq:lemma2-1}
\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
\end{equation}
\begin{equation}\label{eq:lemma2-2}
\mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] \leq \mathbb{E}_q\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_q\left[ \text{v}(\bm{w}) \right] + \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{equation}
\end{lemma}
\begin{proof}
From Hoeffding's inequality we have:
\begin{align*}
P\left( \abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} > \epsilon \right) \leq 2\exp\left( -\frac{2N\epsilon^2}{\left(2\frac{R_{max}}{1-\gamma}\right)^4} \right)
\end{align*}
which implies that, for any $\delta>0$, with probability at least $1-\delta$:
\begin{align*}
\abs{\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
Under independence assumptions, the expected TD error can be re-written as:
\begin{align*}
\mathbb{E}_{\nu,\mathcal{P}}\left[\norm{\wt B_{\bm{w}}}_D^2\right] =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \mm_{a'} Q_{\bm{w}}(s_i',a') - Q_{\bm{w}}(s_i,a_i))^2\right]\\ =\ & \mathbb{E}_{\nu,\mathcal{P}}\left[(R(s,a) + \gamma \mm_{a'} Q_{\bm{w}}(s',a') - Q_{\bm{w}}(s,a))^2\right]\\ =\ & \mathbb{E}_{\nu}\left[\mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}^2\right]\right]\\ =\ & \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right] + \mathbb{E}_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]^2\right]\\ =\ & v(\bm{w}) + \norm{\wt B_{\bm{w}}}_{\nu}^2,
\end{align*}
where $v(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Thus:
\begin{align}\label{eq:hoeff}
\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \leq 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align}
From the change of measure inequality \cite{seldin2012pac}, we have that, for any measurable function $f(\bm{w})$ and any two probability measures $p$ and $q$:
\begin{align*}
\log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \geq \mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p).
\end{align*}
Thus, multiplying both sides of \eqref{eq:hoeff} by $\lambda^{-1}N$ and applying the change of measure inequality with $f(\bm{w}) = \lambda^{-1}N\abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2}$, we obtain:
\begin{align*}
\mathbb{E}_q\left[ f(\bm{w}) \right] - KL(q||p) \leq \log\mathbb{E}_p\left[e^{f(\bm{w})}\right] \leq 4\frac{R_{max}^2 \lambda^{-1}N}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since the right-hand side of \eqref{eq:hoeff} does not depend on $\bm{w}$. Finally, we can explicitly write:
\begin{align*}
\mathbb{E}_q\left[ \abs{\norm{\wt B_{\bm{w}}}_{\nu}^2 + v(\bm{w}) - \norm{\wt B_{\bm{w}}}_D^2} \right] \leq \frac{\lambda}{N} KL(q||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}
\end{align*}
from which the lemma follows straightforwardly.
\end{proof}

@@

\begin{lemma}\label{lemma:general-bound}
Fix a task $\mathcal{M}_{\tau}$. Let $p$ be a prior distribution over weights $\bm{w}$, and $\nu$ be a probability measure over $\mathcal{S}\times\mathcal{A}$. Assume $\wh{\xi}$ is the minimizer of \eqref{eq:elbo} for a dataset $D$ of $N$ i.i.d. samples where state-action couples are distributed according to $\nu$. Define $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$. Then, for any $\delta > 0$, with probability at least $1-\delta$:\todo{Make sure that the constants multiplying sqrt are correct now}
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
\end{lemma}
\begin{proof}
Let us use Lemma \ref{lemma:l2} for the specific choice $q=q_{\wh{\xi}}$. From Eq. \eqref{eq:lemma2-1}, we have:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] - \mathbb{E}_{q_{\wh{\xi}}}\left[ v(\bm{w}) \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ \leq\ & \mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\wh{\xi}}}||p) + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\\ =\ & \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right] + \frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 4\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align*}
where the second inequality holds since $v(\bm{w}) > 0$, while the equality holds from the definition of $\wh{\xi}$. We can now use Eq. \eqref{eq:lemma2-2} to bound $\mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_D^2 \right]$, thus obtaining:
\begin{align*}
\mathbb{E}_{q_{\wh{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq \inf_{\xi \in \Xi}\left\{ \mathbb{E}_{q_{\xi}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\xi}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\xi}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}.
\end{align*}
This concludes the proof.
\end{proof}

@@

\begin{restatable}{theorem}{thg} \label{th:main-gaussian}
Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator. Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_{2}\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_{2}\leq \phi_{\max}$. Consider the Gaussian version of Algorithm~\ref{alg:transfer} with prior $p(\bm{w}) =\mathcal{N}(\bm{\mu}_p,\bm{\Sigma}_p)$ and denote by $(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ the variational parameter minimizing the objective of Eq.~\eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d. samples distributed according to $\tau$ and $\nu$. Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}}\left[\wt B_{\bm{w}}\right]\right]$. Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \mathcal{N}(\wh{\bm{\mu}},\wh{\bm{\Sigma}})$ and dataset $D$:
\begin{equation}
\resizebox{0.93\textwidth}{!}{$
\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}} + \frac{c_2 + \lambda d \log N + \lambda\norm{\bm{w}^* - \bm{\mu}_p}_{\bm{\Sigma}_p^{-1}}}{N} + \frac{c_3}{N^2}\right)$}.
\end{equation}
\end{restatable}
\begin{proof}
Using Lemma \ref{lemma:general-bound} with variational parameters $\wh{\bm{\xi}} = (\wh{\bm{\mu}},\wh{\bm{\Sigma}})$, we have:
\begin{align}\label{eq:thg-4}
\mathbb{E}_{q_{\wh{\bm{\xi}}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] \leq\ & \inf_{\bm{\xi} \in \Xi}\left\{ \mathbb{E}_{q_{\bm{\xi}}}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{q_{\bm{\xi}}}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL({q_{\bm{\xi}}}||p) \right\} + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}}\notag\\ \leq\ & \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ \norm{\wt B_{\bm{w}}}_{\nu}^2 \right ] + \mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[ v(\bm{w}) \right] + 2\frac{\lambda}{N} KL\left(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p\right)\notag\\ &\ \ + 8\frac{R_{max}^2}{(1-\gamma)^2}\sqrt{\frac{\log\frac{2}{\delta}}{2N}},
\end{align}
where the second inequality is due to the fact that, since Lemma \ref{lemma:general-bound} contains an infimum over the variational parameters, we can upper bound its right-hand side by choosing any specific $\bm{\xi}$ from $\Xi$. Here, we choose $\bm{\mu} = \bm{w}^*$ and $\bm{\Sigma} = c\bm{I}$, for some positive constant $c>0$. Let us now bound these terms separately.

@@

\mathbb{E}_{\mathcal{N}(\bm{w}^*,c\bm{I})}\left[\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2\right] \leq 2\norm{\wt{B}_{\bm{w}^*}}_{\nu}^2 + \frac{1}{2}\gamma^2\kappa^2 c^2\bm{\phi}_{max}^4 + c\left(\bm{w}_{max}\bm{\phi}_{max}(1 + \gamma)\right)^2.

@@

Fix a target task $\mathcal{M}_{\tau}$ and let $\wt{Q}$ be the fixed-point of the corresponding mellow Bellman operator. Assume linearly parameterized value functions $Q_{\bm{w}}(s,a)=\bm{w}^T\bm{\phi}(s,a)$ with bounded weights $\norm{\bm{w}}_2\leq w_{max}$ and uniformly bounded features $\norm{\bm{\phi}(s,a)}_2\leq \phi_{\max}$. Consider the mixture version of Algorithm~ \ref{alg:transfer} using $C$ components, source task weights $\mathcal{W}_s$, and bandwidth $\sigma^2_p\ $ for the prior. Denote by $\wh{\bm{\xi}} = (\wh{\bm{\mu}}_1,\dots,\wh{\bm{\mu}}_C,\wh{\bm{\Sigma}}_1,\dots,\wh{\bm{\Sigma}}_C)$ the variational parameters minimizing the objective of Eq. \eqref{eq:elbo} on a dataset $D$ of $N$ i.i.d. samples distributed according to $\tau$ and $\nu$. Let $\bm{w}^* = \arginf_{\bm{w}}\norm{\wt{B}_{\bm{w}}}_{\nu}^2$ and define $\upsilon(\bm{w}^*) \triangleq \mathbb{E}_{\mathcal{N}(\bm{w}^*,\frac{1}{N}\bm{I})}\left[ \text{v}(\bm{w}) \right]$, with $\text{v}(\bm{w}) \triangleq \mathbb{E}_{\nu}\left[Var_{\mathcal{P}_{\tau}}\left[\wt B_{\bm{w}}\right]\right]$. Then, there exist constants $c_1,c_2,c_3$ such that, with probability at least $1-2\delta$ over the choice of weights $\bm{w} \sim \frac{1}{C}\sum_i\mathcal{N}(\wh{\bm{\mu}}_i,\wh{\bm{\Sigma}}_i)$ and dataset $D$:

@@

\resizebox{0.92\textwidth}{!}{$
\norm{Q_{\bm{w}} - \wt{Q}}_{\nu}^2 \leq \frac{1}{(1-\gamma)\delta}\left(2\norm{\wt{B}_{\bm{w}^{*}}}_{\nu}^2 + \upsilon(\bm{w}^*) + c_1\sqrt{\frac{\log\frac{2}{\delta}}{N}}  + \frac{c_2 +  \lambda d \log N + 2\lambda\varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right)}{N} + \frac{c_3}{N^2}\right)$},

@@

where, for a vector $\bm{x} = (x_1,\dots,x_d)$, $\varphi \left( x_j\right) \triangleq \sum_i \frac{e^{-x_i}}{\sum_j e^{-x_j}}x_i$ is the \textit{softmin} function.

@@

where the inequality holds since the first term is negative. For the second term of \eqref{eq:thmg-2}:

@@

KL(\mathcal{N}(\bm{w}^*,c\bm{I})\ ||\ p) \leq \log\abs{\mathcal{W}_s} + \frac{1}{2}d\log\frac{\sigma^2_p}{c} + \frac{1}{2}d\frac{c}{\sigma^2_p} + \varphi\left(\frac{1}{2\sigma^2_p}\norm{\bm{w}^* - \bm{w}_j}\right).
